% --- LaTeX CV Template - S. Venkatraman ---

% Set document class and font size
\documentclass[letterpaper, 11pt]{article}
\usepackage[utf8]{inputenc}

% Package imports
\usepackage{setspace, longtable, graphicx, hyphenat, hyperref, fancyhdr, ifthen, everypage, enumitem, amsmath, setspace}

% --- Page layout settings ---

% Set page margins
\usepackage[left=1in, right=1in, bottom=0.7in, top=0.7in]{geometry}

% Set line spacing
\renewcommand{\baselinestretch}{1.15}

% --- Page formatting ---

% Set link colors
\usepackage[dvipsnames]{xcolor}
\hypersetup{colorlinks=true, linkcolor=RoyalBlue, urlcolor=RoyalBlue}

% Set font to Libertine, including math support
\usepackage{libertine}
\usepackage[libertine]{newtxmath}

% Remove page numbering
\pagenumbering{gobble}

% --- Document starts here ---

\begin{document}

% Name and date of last update to this document
\noindent{\Huge{Lizaveta Shelianhouskaya}}

% --- Contact information and other items ---

\vspace{0.5cm} 
\begin{center}
\begin{tabular}{lll}
% Line 1: Email, GitHub, office location
\textbf{Email}: liza.shelengovskaya22@gmail.com      &
\hspace{0.1in} \textbf{GitHub}: shelengovskaya   
 % &
% \hspace{0.1in} 	\textbf{Date of birth}: 22.06.2002 \\

% Line 2: Phone number, citizenship
% \textbf{Phone}: +375447401309   & 
% \hspace{0.1in} 
% \textbf{Citizenship}: Belarus 
\end{tabular}
\end{center}

% --- Start the two-column table storing the main content ---

% Set spacing between columns
\setlength{\tabcolsep}{4pt}

% Set the width of each column
\begin{longtable}{p{1.3in}p{4.8in}}

% --- Section: Research interests ---

% \nohyphens{\color{OliveGreen}{Objective}}
% & Hard-working and motivated Computer Science student seeking an internship to utilize my
% education while gaining valuable work experience in a team. \\
% & \\



% --- Section: Work experience ---

\color{OliveGreen}{Work experience}
& \textbf{Yandex} \hfill Moscow, Russia \\ 
& Software developer \hfill November 2021--Present \\
& Cloud security department \\
& \\


& \textbf{Aton} \hfill Moscow, Russia \\ 
& Junior specialist \hfill August--October 2021 \\
& Information support department \\
& \\




% --- Section: Education ---

\color{OliveGreen}{Education} 
& \textbf{Higher School of Economics} \hfill Moscow, Russia \\ 
& Advanced training \hfill April 2023--June 2023 \\
& Methods and means of protection against
cyber threats\\
& \\

& \textbf{Higher School of Economics} \hfill Moscow, Russia \\ 
& Bachelor of Computer Science \hfill September 2019--June 2023 \\
& Applied Mathematics and Information Science\\
& GPA 7.46/10 \\
% & Expected graduation date 2023 \\
& \\

& \textbf{Secondary School №14} \hfill Molodechno, Belarus \\
& Profile: Mathematics, Physics. \hfill 2008--2019\\
& GPA 10/10 \\
& \\



{\color{OliveGreen}{Additional}}
& \textbf{Software Development course (Itransition)} \hfill Minsk, Belarus\\
{\color{OliveGreen}{Education}} 
& Java / Spring / JavaScript / MySQL \hfill January--February 2021\\
& \\

& \textbf{Summer Camp Profile “BIT”} \\
& Learning C++, Algorithms and Data Structures \hfill July 2018, June 2017 \\
& \\

% & \textbf{Children’s Music School} \hfill Molodechno, Belarus\\
% & Class Piano Program\hfill 2010--2017\\
% & \\


{\color{OliveGreen}{Aware and}} 
& III diploma in the Belarusian Republican Olympiad in Informatics,\hfill 2019\\
{\color{OliveGreen}{achievements}} 
& 3rd stage \\
& III diploma in the Global Scholarship Competition in Mathematics \hfill 2018\\
& 3rd place in the Republican Internet-Olympiad in Informatics  \hfill 2017\\
& \\

% --- Section: Publications ---
\nohyphens{\color{OliveGreen}{Technical skills}}
& 1. Knowledge of C++, Java, Python, Golang. \\
& 2. Experience with the Qt (C++) and Spring (Java) frameworks. \\
& 3. Flexible with the build environments Linux, Windows. \\
& 4. Familiarity with the use of Vim, CLion, PyCharm, MC Office, Google Disk. \\
& 5. Knowledge of Algorithms and Data Structures. \\
& 6. Experience in Object Oriented concepts. \\
& \\

% --- Section: Research experience ---

\nohyphens{\color{OliveGreen}{Soft skills}} 
& Fast Learning \hfill Organizational skills \\
& Creativity \hfill Communication Skills \\
& Time-management \hfill Problem-Solving \\
& \\

% --- Section: Talks and tutorials ---

{\color{OliveGreen}{Languages}} 
& Russian (native) \\
& Belarusian (native) \\
& English (fluent) \\
& Italian (beginner)
& \\

% --- Section: Other interests/hobbies ---

\nohyphens{\color{OliveGreen}{Other interests}} 
& 1. Reading the books. \\
& 2. Playing the piano. \\
& 3. Exploring distant lands.\\

% --- End of CV! ---

\end{longtable}
\end{document}
